An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
better wording for last part
better wording for Example 1

\para{Example~1: Ordering errors.} 
The first example configuration error is first reported by 
Yin {\em et al.}~\cite{yin11anempirical}.
For instance, when a user configures PHP to run with the
Apache HTTP Server, this user may write, among others, 
the following lines in the configuration file.

@@

If this user is using \app, she can avoid such a configuration error.
In particular, \app is able to inform the user that {\tt recode.so} 
should appear before {\tt mysql.so} and reports the error (as shown
below).

@@

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
A configuration error reported recently made the MySQL
daemon fail to start~\cite{syserror}.
One entry was written as 
{\tt datadir=/root/appfinder/mysql}, and the type, as well as 
format, seemed correct.
However, the problem is that this directory should not 
contain the root directory; the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called a system environment-related configuration error.
Both \app and EnCore can handle misconfigurations concerning system execution.
Furthermore, \app is also able to detect type and syntax errors
in configuration files.

>>>>

\para{Example~1: Ordering errors.} 
The first class of configuration errors we handle was first reported by 
Yin {\em et al.}~\cite{yin11anempirical}.
For instance, when a user configures PHP to run with the
Apache HTTP Server, this user might write, amongst others, 
the following lines in the configuration file.

@@

By using \app, the user can avoid such a configuration error.
In particular, \app is able to inform the user that {\tt recode.so} 
should appear before {\tt mysql.so}, as shown
below.

@@

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
A recently reported configuration error made the MySQL
daemon fail to start~\cite{syserror}.
One entry was written as 
{\tt datadir=/root/appfinder/mysql}, and the type, as well as 
format, seemed correct.
However, the problem is that this directory should not 
contain the root directory; the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called a system environment-related configuration error.
Both \app and EnCore can handle misconfigurations concerning system execution.
Furthermore, \app is also able to detect type and syntax errors
in configuration files.
